04_analysis

### 2023-08-16 04_analysis.Rmd
added code to save allDrifts as rda

Bind ALL DRIFTS into one dataframe
```{r}
allDrifts <- rbind(fulltrack07, fulltrack08, fulltrack10, fulltrack12, fulltrack13, fulltrack14, 
                   fulltrack16, fulltrack18, fulltrack19, fulltrack20, fulltrack21, fulltrack22, fulltrack23)
```

>>>>

Bind ALL DRIFTS into one dataframe
```{r}
allDrifts <- rbind(fulltrack07, fulltrack08, fulltrack10, fulltrack12, fulltrack13, fulltrack14, 
                   fulltrack16, fulltrack18, fulltrack19, fulltrack20, fulltrack21, fulltrack22, fulltrack23)
#save(allDrifts, file = "allDrifts.rda")
```
